---
title: "vodafone-analysis"
author: "ahmed-akram"
date: "May 23, 2016"
output: html_document
---

```{r}
library(dplyr)
library(ggplot2)
```

```{r reading data, message=FALSE, comment=NA, cache=TRUE}

# library(plyr)
library(e1071)
library(rpart)
library(randomForest)
library(neuralnet)
library(dplyr)
library(ipred)

library(ggplot2)
library(RWeka)
library(forecast)
set.seed(10)


model_train <- read.csv("data/train.csv")
model_test <- read.csv("data/test.csv")
calender_ref <- read.csv("data/calendar_ref.csv")
contract_ref <- read.csv("data/contract_ref.csv")
# daily <- read.csv("data/daily_aggregate.csv")
```

## renaming columns

```{r renaming columns, cache=TRUE}
model_train <- model_train %>% dplyr::rename(
    MONTH1_USAGE = X206_USAGE,
    MONTH2_USAGE = X207_USAGE,
    MONTH3_USAGE = X208_USAGE,
    MONTH4_USAGE = X209_USAGE,
    MONTH5_USAGE = X210_USAGE,
    MONTH1_SESSIONS = X206_SESSION_COUNT,
    MONTH2_SESSIONS = X207_SESSION_COUNT,
    MONTH3_SESSIONS = X208_SESSION_COUNT,
    MONTH4_SESSIONS = X209_SESSION_COUNT,
    MONTH5_SESSIONS = X210_SESSION_COUNT
)

model_test <- model_test %>% dplyr::rename(
    MONTH1_USAGE = X206_USAGE,
    MONTH2_USAGE = X207_USAGE,
    MONTH3_USAGE = X208_USAGE,
    MONTH4_USAGE = X209_USAGE,
    MONTH5_USAGE = X210_USAGE,
    MONTH1_SESSIONS = X206_SESSION_COUNT,
    MONTH2_SESSIONS = X207_SESSION_COUNT,
    MONTH3_SESSIONS = X208_SESSION_COUNT,
    MONTH4_SESSIONS = X209_SESSION_COUNT,
    MONTH5_SESSIONS = X210_SESSION_COUNT
)
```

## adding the total usage, total sessions and avg usage per session
```{r adding totals, cache=TRUE}
add_totals <- function(data) {
	data$TOTAL_USAGE <- data %>% apply(1, function(row) {
	return(row[['MONTH1_USAGE']] + row[['MONTH2_USAGE']] + row[['MONTH3_USAGE']] + row[['MONTH4_USAGE']] + row[['MONTH5_USAGE']])
})	
	
	data$TOTAL_SESSIONS <- data %>% apply(1, function(row) {
	return(row[['MONTH1_SESSIONS']] + row[['MONTH2_SESSIONS']] + row[['MONTH3_SESSIONS']] + row[['MONTH4_SESSIONS']] + row[['MONTH5_SESSIONS']])
})
	
	data$AVG_PER_SESSION <- data %>% apply(1, function(row) {
	return(row[['TOTAL_USAGE']] / row[['TOTAL_SESSIONS']])
})
	
	data
}

model_train <- add_totals(model_train)
model_test <- add_totals(model_test)
```


```{r adding the roaming counter to datasets, cache=TRUE}
daily_roaming_counter <- daily %>% group_by(CONTRACT_KEY) %>% summarise(roaming_counter = sum(as.numeric(ROAMING_FLAG)))

hash<-new.env()
for(i in 1:(daily_roaming_counter %>% nrow)) {
	hash[[as.character(daily_roaming_counter[i,]$CONTRACT_KEY)]] <- daily_roaming_counter[i,]$roaming_counter
}

add_roaming_counter <- function(data) {
	data$ROAMING_COUNTER <- data %>% apply(1, function(row) {
		if(is.null(hash[[as.character(row[['CONTRACT_KEY']])]])) {
			return(NA)
		}
		return(hash[[as.character(row[['CONTRACT_KEY']])]])
	})
	data
}

model_train <- add_roaming_counter(model_train)
model_test <- add_roaming_counter(model_test)
```


```{r adding the diff features, cache=TRUE}
add_differences <- function(data) {
	subtrain <- data
	subtrain$diff_one2 <- subtrain %>% apply(1, function(x) {
		(x[['MONTH3_USAGE']] / mean(c(x[['MONTH1_USAGE']], x[['MONTH2_USAGE']]))) * 100
	})
	
	subtrain$diff_two2 <- subtrain %>% apply(1, function(x) {
		(x[['MONTH4_USAGE']] / mean(c(x[['MONTH2_USAGE']], x[['MONTH3_USAGE']]))) * 100
	})
	
	subtrain$diff_three2 <- subtrain %>% apply(1, function(x) {
		(x[['MONTH5_USAGE']] / mean(c(x[['MONTH3_USAGE']], x[['MONTH4_USAGE']]))) * 100
	})

	subtrain
}

add_differences2 <- function(data) {
	subtrain <- data
	subtrain$diff_one <- subtrain %>% apply(1, function(x) {
		if(x[['MONTH3_USAGE']] > mean(c(x[['MONTH1_USAGE']], x[['MONTH2_USAGE']])) + 500) {
			return(1)
		}
		return(0)
	})
	
	subtrain$diff_two <- subtrain %>% apply(1, function(x) {
		if(x[['MONTH4_USAGE']] > mean(c(x[['MONTH2_USAGE']], x[['MONTH3_USAGE']])) + 500) {
			return(1)
		}
		return(0)
	})
	
	subtrain$diff_three <- subtrain %>% apply(1, function(x) {
		if(x[['MONTH5_USAGE']] > mean(c(x[['MONTH3_USAGE']], x[['MONTH4_USAGE']])) + 500) {
			return(1)
		}
		return(0)
	})
	subtrain
}

model_train <- add_differences(model_train)
model_train <- add_differences2(model_train)

model_test <- add_differences(model_test)
model_test <- add_differences2(model_test)
```

## adding mean usage and the number of times the user exceeded his/her average in past months
```{r mean usage and number of times exceeding, cache=TRUE}
model_train <- model_train %>% mutate(SUM_EXCEEDING = diff_one + diff_two + diff_three)
model_train <- model_train %>% mutate(MEAN_USAGE = TOTAL_USAGE / 5)

model_test <- model_test %>% mutate(SUM_EXCEEDING = diff_one + diff_two + diff_three) %>% mutate(MEAN_USAGE = TOTAL_USAGE / 5)
```

## weighted average method to predict the usage of the 6th month
```{r weighted average and a feature influenced from the graph, cache=TRUE}
model_train <- model_train %>% mutate(WEIGHTED_AVG = (5*MONTH5_USAGE + 4*MONTH4_USAGE + 3*MONTH3_USAGE + 2*MONTH2_USAGE + MONTH1_USAGE) / 15)

model_test <- model_test %>% mutate(WEIGHTED_AVG = (5*MONTH5_USAGE + 4*MONTH4_USAGE + 3*MONTH3_USAGE + 2*MONTH2_USAGE + MONTH1_USAGE) / 15)

model_test <- model_test %>% mutate(DIFF_BETWEEN_6th_AND_MEAN = WEIGHTED_AVG - MEAN_USAGE)

model_train <- model_train %>% mutate(DIFF_BETWEEN_6th_AND_MEAN = WEIGHTED_AVG - MEAN_USAGE)

model_train <- model_train %>% mutate(BIGGER_THAN = as.numeric(DIFF_BETWEEN_6th_AND_MEAN) > 105)

model_test <- model_test %>% mutate(BIGGER_THAN = as.numeric(DIFF_BETWEEN_6th_AND_MEAN) > 105)

model_train$BIGGER_THAN <- as.numeric(model_train$BIGGER_THAN)
model_test$BIGGER_THAN <- as.numeric(model_test$BIGGER_THAN)
```

## merging the train and test datasets with the contract_ref to fll up the information
```{r}
model_train <- merge(x = model_train, y = contract_ref, by = 'CONTRACT_KEY')
model_test <- merge(x = model_test, y = contract_ref, by = 'CONTRACT_KEY')
```

## renaming all gender data to 'Male', 'Female' or 'NA' 
```{r}
rename_gender <- function(data) {
data$GENDER[data$GENDER == 'M'] <- 'Male'
data$GENDER[data$GENDER == 'm'] <- 'Male'
data$GENDER[data$GENDER == 'F'] <- 'Female'
data$GENDER[data$GENDER == 'f'] <- 'Female'
data$GENDER[data$GENDER == 'Unknown'] <- NA
data$GENDER[data$GENDER == 'Not Entered'] <- NA
data$GENDER <- factor(data$GENDER)
return(data)
}

model_test <- rename_gender(model_test)
model_train <- rename_gender(model_train)

model_train$VALUE_SEGMENT[model_train$VALUE_SEGMENT == 'N/A'] <- NA
model_train$VALUE_SEGMENT <- factor(model_train$VALUE_SEGMENT)
```

plotting the Total Usage against the Total Sessions (taking a subset of the data to remove the extreme outliers to better fir the plot)
Figure(1)
```{r, cache=TRUE}
model_train %>% 
	subset(TOTAL_USAGE < 100000) %>% subset(TOTAL_SESSIONS < 20000) %>% 
	ggplot(aes(x=TOTAL_SESSIONS, y=TOTAL_USAGE)) + 
	geom_point(aes(color=factor(TARGET))) +
	scale_color_manual("Target\n",labels = c("0", "1"), values = c("#EFADA9", "#69B5C7")) +
	theme(axis.title.y = element_text(size=12,angle=0,hjust=0.5,vjust=1,lineheight=40)) +
	labs(title="Total usage for 5 months vs. Total number of sessions (Figure 1)", x="Total Number of Sessions", y="5 Months Total Usage")

```


```{r, cache=TRUE}
model_train %>% 
	subset(TOTAL_SESSIONS < 10000) %>% subset(AVG_PER_SESSION < 500) %>% 
	ggplot(aes(x=TOTAL_SESSIONS, y=AVG_PER_SESSION)) + 
	geom_point(aes(color=factor(TARGET))) +
	scale_color_manual("Target\n",labels = c("0", "1"), values = c("#EFADA9", "#69B5C7")) +
	theme(axis.title.y = element_text(size=12,angle=0,hjust=0.5,vjust=1,lineheight=40)) +
	labs(title="Average usage per session vs. Total number of sessions (Figure 2)", x="Total Number of Sessions", y="Usage Per Session")
```


Total usage density:
```{r Total usage density, cache=TRUE}
model_train %>% 
	subset(TOTAL_USAGE < 75000) %>% 
	ggplot(aes(TOTAL_USAGE, fill=factor(TARGET))) +
	scale_fill_manual("Target\n",labels = c("0", "1"), values = c("#EFADA9", "#69B5C7")) +
    geom_density(alpha=I(0.7)) +
	theme(axis.title.y = element_text(size=12,angle=0,hjust=0.5,vjust=1,lineheight=40)) + 
	labs(title="Density of total usage for 5 months (Figure 3)", x="Total usage for 5 months", y="Density")
```


Average per session density:
```{r Average per session density, cache=TRUE}
model_train %>% 
	subset(AVG_PER_SESSION < 25) %>% 
	ggplot(aes(AVG_PER_SESSION, fill=factor(TARGET))) +
	scale_fill_manual("Target\n",labels = c("0", "1"), values = c("#EFADA9", "#69B5C7")) +
    geom_density(alpha=I(0.7)) +
	theme(axis.title.y = element_text(size=12,angle=0,hjust=0.5,vjust=1,lineheight=40)) + 
	labs(title="Density of average usage per session (Figure 4)", x="Average Usage Per Session", y="Density")
```


Weighted average vs. Average usage:
```{r Weighted average vs. Average usage, cache=TRUE, fig.width=11, fig.height=8}
model_train %>% 
	subset(MEAN_USAGE < 10000) %>% 
	ggplot(aes(x=MEAN_USAGE, y=WEIGHTED_AVG)) + 
	geom_point(aes(color=factor(TARGET))) +
	scale_color_manual("Target\n",labels = c("0", "1"), values = c("#EFADA9", "#69B5C7")) +
	theme(axis.title.y = element_text(size=12,angle=0,hjust=0.5,vjust=1,lineheight=40)) +
	theme(axis.text.x = element_text(size=10,angle=45)) +
	theme(axis.title.x = element_text(size=12)) +
	theme(plot.title = element_text(size=12)) +
	scale_x_continuous(breaks = floor(seq(min(model_train$MEAN_USAGE), max(model_train$MEAN_USAGE), by = 500))) +
  	scale_y_continuous(breaks = floor(seq(min(model_train$WEIGHTED_AVG), max(model_train$WEIGHTED_AVG), by = 1000))) +
	labs(title = "Forecasted 6th month vs. Mean of 5 months (Figure 5)", x="5 Months Mean Usage", y="6th Month usage")
```

Figure(6)
```{r Density of forecasted - mean, cache=TRUE, fig.width=12, fig.height=7}
model_train %>% 
	subset(DIFF_BETWEEN_6th_AND_MEAN < 500) %>% 
	subset(DIFF_BETWEEN_6th_AND_MEAN > -500) %>%
	ggplot(aes(DIFF_BETWEEN_6th_AND_MEAN, fill=factor(TARGET))) +
	scale_fill_manual("Target\n",labels = c("0", "1"), values = c("#EFADA9", "#69B5C7")) +
    geom_density(alpha=I(0.7)) +
	theme(axis.title.y = element_text(size=12,angle=0,hjust=0.5,vjust=1,lineheight=40)) +
	theme(axis.title.x = element_text(size=12)) +
	theme(axis.text.x = element_text(size=10,angle=45)) + 
	theme(plot.title = element_text(size=13,angle=0)) + 
	labs(title = "Density for (6th_Month - Five_Months_Avg) (Figure 6)", x="Difference between forecasted 6th month and average", y="Density") + 
	scale_x_continuous(breaks = ceiling(seq(min(model_train$DIFF_BETWEEN_6th_AND_MEAN), max(model_train$DIFF_BETWEEN_6th_AND_MEAN), by = 25)))
```

<!-- Weighted average vs. Average usage: -->
```{r Diff vs. Avg per session, cache=TRUE, fig.width=13, echo=FALSE}
model_train %>% 
	subset(AVG_PER_SESSION < 1000) %>%
	subset(TOTAL_SESSIONS < 50000) %>% 
	subset(DIFF_BETWEEN_6th_AND_MEAN < 1000) %>%
	subset(DIFF_BETWEEN_6th_AND_MEAN > -1000) %>%
	ggplot(aes(x=DIFF_BETWEEN_6th_AND_MEAN, y=TOTAL_SESSIONS)) +
	geom_point(aes(color=factor(TARGET))) +
	scale_color_manual("Target\n",labels = c("0", "1"), values = c("#EFADA9", "#69B5C7")) +
	theme(axis.title.y = element_text(size=14,angle=0,hjust=0.5,vjust=1,lineheight=40)) +
	theme(axis.text.x = element_text(size=12,angle=45)) +
	theme(axis.title.x = element_text(size=14)) +
	theme(plot.title = element_text(size=14)) +
	scale_x_continuous(breaks = floor(seq(-1000, 1000, by = 100))) +
	labs(title = "Diff between 6th month and mean vs. Number of sessions (Figure 7)", x="Diff Between 6th and Mean", y="Total Sessions")
```

<!-- Figure(7) -->
<!-- ```{r Density of forecasted - mean, cache=TRUE, fig.width=12, fig.height=7} -->
<!-- model_train %>%  -->
<!-- 	subset(TARGET == 0) %>% -->
<!-- 	ggplot(aes(RATE_PLAN, fill=factor(TARGET))) + -->
<!-- 	scale_fill_manual("Target\n",labels = c("0", "1"), values = c("#EFADA9", "#69B5C7")) + -->
<!--     stat_count(alpha=I(0.7)) + -->
<!-- 	theme(axis.title.y = element_text(size=12,angle=0,hjust=0.5,vjust=1,lineheight=40)) + -->
<!-- 	theme(axis.title.x = element_text(size=12)) + -->
<!-- 	theme(axis.text.x = element_text(size=10,angle=45)) +  -->
<!-- 	theme(plot.title = element_text(size=13,angle=0)) +  -->
<!-- 	labs(title = "Density for (6th_Month - Five_Months_Avg) (Figure 6)", x="Difference between forecasted 6th month and average", y="Density") +  -->
<!-- 	scale_x_discrete(breaks = seq(1,179, by = 1)) -->
<!-- ``` -->
